Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-09-09 Report/problem_formulation.tex
Modifications made for the convergence
revision - 1

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value. Eq. \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2
\end{equation}
It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure-approx} if the second order terms are ignored. Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation. In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system. The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \ac{Q-WSRM} approach.

>>>>

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value. In fact, Eq. \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2
\end{equation}
It is evident that \eqref{pf-1} is equivalent to \eqref{backpressure-approx} if the second order terms are ignored. Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation. In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system. The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in \ac{Q-WSRME} approach.

### 2014-09-09 Report/problem_formulation_intro.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
revision - 1

To minimize the total number of backlogged packets, we consider minimizing \me{\ell_{q}}-norm of all the queue deviation given by
\begin{equation}
v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}).
\label{eqn-4.2}
\end{equation}
Explicitly, the considered problem is given by \me{\sum_{k \in \mc{U}} \, | v_k |^q}. With this objective, the problem of weighted queued packet minimization is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively. It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users. In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels. Before discussing the proposed solutions, we consider the existing algorithm to solve the issue of minimizing the number of backlogged packets with additional constraints required by problem.

For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
\begin{equation}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
\begin{itemize}
\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

>>>>

To minimize the total number of backlogged packets, we consider minimizing weighted \me{\ell_{q}}-norm of all the queue deviation given by
\begin{equation}
v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
\label{eqn-4.2}
\end{equation}
Explicitly, the considered problem is given by \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. With this objective, the problem of weighted queued packet minimization is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}. In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.

For practical and tractability reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

Before proceeding further, we note that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
\begin{itemize}
\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

### 2014-09-09 Report/simulation_distributed.tex
revision - 1

In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{[0,-6]} dB. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

@@

Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method is not converged to the optimal point but oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{fig-9-2}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3.1}
\end{figure}

The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot. The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables are not allowed to converge in between the \ac{SCA} steps in the \ac{KKT} approach. In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}. The figure compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRM} scheme compared to the \me{\ell_2} norm which includes it. By dropping the squared rate variable, the \ac{Q-WSRM} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues. On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

>>>>

In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to be scattered over the cell boundary experiencing the path loss following the uniform distribution between \me{[0,-6]} dB. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

@@

Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{fig-9-2}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3.1}
\end{figure}

The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot. The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach. In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}. Fig. \ref{fig-d-3.1} also compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it. By dropping the squared rate variable, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues. On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-09-09 Report/simulation_results.tex
revision - 1

This section discusses the performance of the centralized algorithms discussed in Section \ref{sec-3} for a few system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively. With this configuration, the resources allocated for the users on each sub-channel by various algorithms are shown in Fig. \ref{tbl-1}.

@@

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The users are located with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-6} dB, thereby simulating a realistic scenario. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRM} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-2}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-2}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently. In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels. At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders. The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig. \ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips. Fig. \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas. As we can see from Fig. \ref{fig-2} that both the optimal and the \ac{MMSE} receiver achieves the same optimal point as compared to the \ac{JSFRA} scheme using \ac{MSE} reformulation. In all the schemes, the receive beamformers are updated at the \ac{SCA} update points instead of updating after the \ac{SCA} convergence as in Algorithm. \ref{algo-1}. Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
\hline
\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
\cline{1-9}
\end{tabular}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{table}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-2}
%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
%\label{tbl-3}
%\end{figure}

The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table. \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas. The configuration is mentioned in the caption of Table. \ref{tbl-3} along with the number of queued bits for each user. It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits. The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets \me{\chi_k = 3.58} bits. The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.

>>>>

In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively.

@@

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The users are located with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-6} dB, thereby simulating a realistic scenario. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-2}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-2}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently. In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels. At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders. The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig. \ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips. Fig. \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas. In all the schemes, the receive beamformers are updated at the \ac{SCA} update points instead of updating after the \ac{SCA} convergence as in Algorithm. \ref{algo-1}. Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
\hline
\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
\cline{1-9}
\end{tabular}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{table}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-2}
%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
%\label{tbl-3}
%\end{figure}

The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table. \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas. The configuration is mentioned in the caption of Table. \ref{tbl-3} along with the number of queued bits for each user. It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits. The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets to be equal for all users to \me{\chi_k = 3.58} bits. The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.
